Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-03-05 manuscript.tex
Move figures

The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
Landing sites which are closer will be considered preferentially over those at a larger distance.
\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{figures/dynamic_exploration/castalia/refine/dist.pdf}}%
    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/dist_masked.pdf}}
    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
\end{figure}
We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{figures/dynamic_exploration/castalia/refine/cost.pdf}
    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
\end{figure}
After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.

>>>>

The next metric is related to the distance from the current spacecraft position to all candidate landing sites on the surface.
We utilize~\cref{eq:geodesic_distance} to compute a distance metric to the surface.
Landing sites which are closer will be considered preferentially over those at a larger distance.
\Cref{fig:distance_castalia_both} shows a surface plot of the distance to the surface. 
The area immediately beneath the spacecraft has a small cost while those on the opposite side of the asteroid have a much larger cost.
\begin{figure}[htbp]
    \centering
    \subcaptionbox{Surface Distance to surface of Castalia\label{fig:surface_distance_castalia}}{\includegraphics[width=0.5\textwidth]{dynamic_exploration_castalia_refine_dist.pdf}}%
    \subcaptionbox{Masked distance to surface with areas \( \phi > \SI{5}{\degree}\) excluded\label{fig:surface_distance_castalia_masked}}{\includegraphics[width=0.5\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_dist_masked.pdf}}
    \caption{Distance to surface of asteroid Castalia\label{fig:distance_castalia_both}}
\end{figure}
We can combine~\cref{fig:distance_castalia_both,fig:surface_slope_castalia_both} to determine the best landing site. 
The combination of the two is shown in~\cref{fig:landing_site_cost} with the desired landing site shown by the blue marker.
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.75\textwidth,keepaspectratio]{dynamic_exploration_castalia_refine_cost.pdf}
    \caption{Total cost for surface landing based on surface slope and distance\label{fig:landing_site_cost}}
\end{figure}
After selecting the appropriate landing site we then prepare for landing by collecting more measurements in the region around the landing area.
